---
title: "Creek Fire Analysis Walkthrough -- KNP Complex Data Check"
output: html_notebook
---

```{r}
library(here)
library(terra)
library(tidyterra)
library(ggplot2)
library(gridExtra)
```

# Check boundary

```{r}
fire_name <- "KNP Complex"
fire_name_clean <- gsub(" ", "_", str_to_lower(fire_name))
boundaries_folder = here("data", fire_name_clean, "boundaries")
buffer_dist <- 10000 # km

fire <- read_sf(here("data", paste0(fire_name_clean, "_fire"), "boundaries", paste0(fire_name_clean, "_fire.geojson")))

fire_buffer <- read_sf(here("data", paste0(fire_name_clean, "_fire"), "boundaries", paste0(fire_name_clean, "_fire_buffer.geojson")))

# Create a bounding box around the fire boundary with buffer
fire_bbox <- get_bbox(fire_name, fire_buffer)

ggplot() +
  geom_spatvector(data = fire_bbox, fill="transparent") +
  geom_spatvector(data = fire$geometry, col="red", fill="transparent") +
  geom_spatvector(data = fire_buffer$geometry, col="blue", fill="transparent") +
  labs(title=paste(fire_name, "Fire Boundary and Buffer"))

```

## OpenET: ensemble ET

```{r}
et_dir <- here(fire_folder_path, "openet")
dir.create(file.path(et_dir))

# Get pre- and post-fire summer months' ET
# Find the fire start date and get the 3 years before it
all_fires <- st_read(here("data", "california_fire_perimeters_all.geojson"))

# Select the fire boundary from all fires
# fire_data <- all_fires[all_fires$FIRE_NAME == str_to_upper(fire_name), ]
fire_data <- all_fires[all_fires$FIRE_NAME == (fire_name), ]

fire_data <- fire_data[which.max(fire_data$GIS_ACRES), ]

start_date <- as.Date(fire_data$ALARM_DATE)
et_date_ranges <- list(seq(as.Date(paste0(as.character(year(start_date)-3), "-06-01")), length.out=2, by="2 month"),
                       seq(as.Date(paste0(as.character(year(start_date)-2), "-06-01")), length.out=2, by="2 month"),
                       seq(as.Date(paste0(as.character(year(start_date)-1), "-06-01")), length.out=2, by="2 month"),
                       seq(as.Date(paste0(as.character(year(start_date)+1), "-06-01")), length.out=2, by="2 month"))

source(here("scripts/openet_processing.R"))

# combine the tiles
combined_tiles <- combine_tiles(et_dir, output_name="full_mosaic", write=TRUE)

prefire_date_values <- as.Date(unlist(lapply(et_date_ranges[1:3], function(x) {seq(from=as.Date(x[1]), to=as.Date(x[-1]), by="1 month")})))

postfire_date_values <- as.Date(unlist(lapply(et_date_ranges[4], function(x) {seq(from=as.Date(x[1]), to=as.Date(x[-1]), by="1 month")})))

prefire_et <- terra::rast(here(et_dir, "tiffs", "prefire_et.tif"))
postfire_et <- terra::rast(here(et_dir, "tiffs", "postfire_et.tif"))

all_vals <- c(terra::global(prefire_et, "min", na.rm = TRUE)$min,
              terra::global(prefire_et, "max", na.rm = TRUE)$max,
              terra::global(postfire_et, "min", na.rm = TRUE)$min,
              terra::global(postfire_et, "max", na.rm = TRUE)$max)

et_min <- min(all_vals)
et_max <- max(all_vals)

# Prefire
prefire_et_plot <- ggplot() +
    geom_spatraster(data = prefire_et, aes(fill = prefire_et)) +
    geom_spatvector(data = fire$geometry, fill = NA, color = "white") +
    geom_spatvector(data = fire_buffer$geometry, fill = NA, color = "yellow") +
    scale_fill_viridis_c(limits = c(et_min, et_max), name="Mean ET (mm)") +
    labs(title = "Pre-fire mean ET") +
    theme_minimal()

# Postfire
postfire_et_plot <- ggplot() +
    geom_spatraster(data = postfire_et, aes(fill = postfire_et)) +
    geom_spatvector(data = fire$geometry, fill = NA, color = "white") +
    geom_spatvector(data = fire_buffer$geometry, fill = NA, color = "yellow") +
    scale_fill_viridis_c(limits = c(et_min, et_max), name="Mean ET (mm)") +
    labs(title = "Post-fire mean ET") +
    theme_minimal()

# Fixed... thank the Lord
grid.arrange(prefire_et_plot, postfire_et_plot, ncol=2)
```


```{r}
# Example for one month
ggplot() +
  geom_spatraster(data = combined_tiles$`2020-07-01`) +
  geom_spatvector(data = fire$geometry, fill = NA, color="white") +
  geom_spatvector(data = fire_buffer, fill = NA, color="yellow") +
    scale_fill_viridis_c(limits = c(et_min, et_max), name="Mean ET (mm)") +
    labs(title = "7/2020 mean ET") +
    theme_minimal()

```

## USGS DEM: elevation
- Features engineered: northness, aspect, slope

```{r}
source(here("scripts/dem_acquisition.R"))

et_ref_path <- here("data", paste0(fire_name_clean,"_fire"), "openet", "tiffs", "full_mosaic.tif")

# Load API key
opentopo_api_key <- Sys.getenv("OPENTOPOGRAPHY_API_KEY")

dem_dir <- here("data", paste0(fire_name_clean,"_fire"), "dem")

output_name <- "usgs_10m_dem"

dem <- terra::rast(here(dem_dir, paste0(output_name, ".tif")))

# Plot it
ggplot() +
  geom_spatraster(data = dem, aes(fill = usgs_10m_dem)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "USGS DEM") +
  scale_fill_viridis_c(name="Elevation (m)") +
  theme_minimal()

```

Now generate slope, aspect, and northness rasters from the elevation data.

```{r}
source(here("scripts/dem_feature_engineering.R"))

dem_path <- here("data", paste0(fire_name_clean,"_fire"), "dem", "usgs_10m_dem.tif")
slope_path <- here("data", paste0(fire_name_clean,"_fire"), "dem", "usgs_10m_slope.tif")
aspect_path <- here("data", paste0(fire_name_clean,"_fire"), "dem", "usgs_10m_aspect.tif")
northness_path <- here("data", paste0(fire_name_clean,"_fire"), "dem", "usgs_10m_northness.tif")

dem_processed_outputs <- list(terra::rast(slope_path), terra::rast(asmpect_path), terra::rast(northness_path))
names(dem_processed_outputs) <- c("slope","aspect","northness")

# Plot the outputs
ggplot() +
  geom_spatraster(data = dem_processed_outputs$slope, aes(fill = slope)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Slope") +
  scale_fill_viridis_c() +
  theme_minimal()

ggplot() +
  geom_spatraster(data = dem_processed_outputs$aspect, aes(fill = aspect)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Aspect") +
  scale_fill_viridis_c() +
  theme_minimal()

ggplot() +
  geom_spatraster(data = dem_processed_outputs$northness, aes(fill = northness)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Northness") +
  scale_fill_viridis_c() +
  theme_minimal()
```

## Harmonized Landsat Sentinel-2: NIR, SWIR2, RED

```{r}
# Check some pieces and scenes
hls_dir <- here(fire_folder_path, "hls")

# Example scene
example_piece <- terra::rast(here(hls_dir, "nir", "pieces",list.files(here(fire_folder_path, "hls", "nir", "pieces"))[10]))
example_scene <- terra::rast(here(hls_dir, "nir",list.files(here(fire_folder_path, "hls", "nir"))[20]))

ggplot() +
  geom_spatraster(data = example_piece$NIR, aes(fill = NIR)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "NIR piece of a scene") +
  scale_fill_viridis_c(name="reflectence") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = example_scene$NIR, aes(fill = NIR)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "NIR full scene") +
  scale_fill_viridis_c(name="reflectence") +
  theme_minimal()
```

- Features engineered: NDVI, NBR, dNDVI, dNBR, dRNBR

```{r}
prefire_ndvi <- terra::rast(here(hls_dir, "mean_prefire_ndvi.tif"))
postfire_ndvi <- terra::rast(here(hls_dir, "mean_postfire_ndvi.tif"))
diff_ndvi <- terra::rast(here(hls_dir, "diff_mean_ndvi.tif"))

prefire_nbr <- terra::rast(here(hls_dir, "mean_prefire_nbr.tif"))
postfire_nbr <- terra::rast(here(hls_dir, "mean_postfire_nbr.tif"))
diff_nbr <- terra::rast(here(hls_dir, "diff_mean_nbr.tif"))

ggplot() +
  geom_spatraster(data = prefire_ndvi$mean_prefire_ndvi, aes(fill = mean_prefire_ndvi)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Mean prefire NDVI") +
  scale_fill_viridis_c(name="(-1,1)") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = postfire_ndvi$mean_postfire_ndvi, aes(fill = mean_postfire_ndvi)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Mean postfire NDVI") +
  scale_fill_viridis_c(name="(-1,1)") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = diff_ndvi$dndvi_mean, aes(fill = dndvi_mean)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Diff. mean NDVI") +
  scale_fill_viridis_c(name="(-2,2)") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = prefire_nbr$mean_prefire_nbr, aes(fill = mean_prefire_nbr)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Mean prefire nbr") +
  scale_fill_viridis_c(name="(-1,1)") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = postfire_nbr$mean_postfire_nbr, aes(fill = mean_postfire_nbr)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Mean postfire nbr") +
  scale_fill_viridis_c(name="(-1,1)") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = diff_nbr$dnbr_mean, aes(fill = dnbr_mean)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Diff. mean nbr") +
  scale_fill_viridis_c(name="(-2,2)") +
  theme_minimal()

```

TerraClimate: monthly precipitation, monthly soil moisture

- Features engineered: 6-month pre-fire precipitation and soil moisture
- Script for downloading from https://www.climatologylab.org/uploads/2/2/1/3/22133936/terraclimate_downloadv2.r

```{r}

buffer_path <- here(boundaries_folder, paste0(fire_name, "_fire_buffer.geojson"))
terraclimate_dir <- here("data", paste0(fire_name_clean,"_fire"), "terraclimate")

# Take a look
prefire_ppt <- terra::rast(here(terraclimate_dir, "prefire_ppt.tif"))
prefire_soil <- terra::rast(here(terraclimate_dir, "prefire_soil.tif"))
prefire_pdsi <- terra::rast(here(terraclimate_dir, "prefire_PDSI.tif"))
prefire_vpd <- terra::rast(here(terraclimate_dir, "prefire_vpd.tif"))
prefire_tmax <- terra::rast(here(terraclimate_dir, "prefire_tmax.tif"))

ggplot() +
  geom_spatraster(data = prefire_ppt$prefire_ppt, aes(fill = prefire_ppt)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Pre-fire 6-mo. mean precipitation") +
  scale_fill_viridis_c(name="mm") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = prefire_soil$prefire_soil, aes(fill = prefire_soil)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Pre-fire 6-mo. mean soil moisture") +
  scale_fill_viridis_c(name="mm") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = prefire_pdsi$prefire_PDSI, aes(fill = prefire_PDSI)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Pre-fire 6-mo. mean PDSI") +
  scale_fill_viridis_c(name="(unitless)") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = prefire_vpd$prefire_vpd, aes(fill = prefire_vpd)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Pre-fire 6-mo. mean VPD") +
  scale_fill_viridis_c(name="kPa") +
  theme_minimal()

ggplot() +
  geom_spatraster(data = prefire_tmax$prefire_tmax, aes(fill = prefire_tmax)) +
  geom_spatvector(data = fire$geometry, fill = NA, col="white") +
  geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
  labs(title = "Pre-fire 6-mo. mean max. temp.") +
  scale_fill_viridis_c(name="Deg. C") +
  theme_minimal()
```


NLDAS: monthly temperature -- **SUPERCEDED** -- now using Terraclimate for maximum 6-moth prefire mean temperature
- Features engineered: 6-month pre-fire temperature
- Downloaded from https://app.climateengine.org/climateEngine (code-based data acquisition is possible, but I haven't prepared it)


```{r}
# tas <- terra::rast(here("data", "nldas", "nldas_prefire_tasmean.tif"))
# 
# ggplot() +
#   geom_spatraster(data = tas$nldas_prefire_tasmean, aes(fill = nldas_prefire_tasmean)) +
#   geom_spatvector(data = fire$geometry, fill = NA, col="white") +
#   geom_spatvector(data = fire_buffer, fill = NA, col="yellow") +
#   labs(title = "Pre-fire 6-mo. mean temperature") +
#   scale_fill_viridis_c() +
#   theme_minimal()
```


# Data Preparation

Having downloaded the data and created derivative features, it's time to ensure that everything has the right extent, projection, and resolution and then put all the relevant data into a data table.

```{r}
# boundaries
boundary <- terra::vect(here("data", "creek_fire", "boundaries", "creek_fire_boundary.geojson"))
buffer <- terra::vect(here("data", "creek_fire", "boundaries", "creek_fire_buffer.geojson"))
terra::expanse(boundary, unit="km")

# dem
elevation <- terra::rast(here("data", "creek_fire", "dem", "usgs_10m_dem.tif"))
northness <- terra::rast(here("data", "creek_fire", "dem", "usgs_10m_northness.tif"))
aspect <- terra::rast(here("data", "creek_fire", "dem", "usgs_10m_aspect.tif"))
slope <- terra::rast(here("data", "creek_fire", "dem", "usgs_10m_slope.tif"))

# hls
dndvi <- terra::rast(here("data", "creek_fire", "hls", "diff_mean_ndvi.tif"))
dnbr <- terra::rast(here("data", "creek_fire", "hls", "diff_mean_nbr.tif"))

# openet
prefire_et <- terra::rast(here("data", "creek_fire", "openet", "tiffs", "prefire_mean_et.tif"))
postfire_et <- terra::rast(here("data", "creek_fire", "openet", "tiffs","postfire_mean_et.tif"))

# terraclimate sm and ppt
sm <- terra::rast(here("data", "creek_fire", "terraclimate", "prefire_soil.tif")) # in mm
ppt <- terra::rast(here("data", "creek_fire","terraclimate", "prefire_ppt.tif"))
pdsi <- terra::rast(here("data", "creek_fire", "terraclimate", "prefire_pdsi.tif"))
vpd <- terra::rast(here("data", "creek_fire", "terraclimate", "prefire_vpd.tif"))
tmax <- terra::rast(here("data", "creek_fire", "terraclimate", "prefire_tmax.tif"))

```

# Run scripts to create models

- Make the big table

```{r}
source(here("scripts","create_table.R"))

fire_folder_path <- here("data", "creek_fire")
buffer_path <- here(fire_folder_path, "boundaries", "creek_fire_buffer.geojson")
boundary_path <- here(fire_folder_path, "boundaries", "creek_fire.geojson")
prefire_et_path <- here(fire_folder_path, "openet", "tiffs", "prefire_mean_et.tif")
postfire_et_path <- here(fire_folder_path, "openet", "tiffs", "postfire_mean_et.tif")
elevation_path <- here(fire_folder_path, "dem", "usgs_10m_dem.tif")
slope_path <- here(fire_folder_path, "dem", "usgs_10m_slope.tif")
aspect_path <- here(fire_folder_path, "dem", "usgs_10m_aspect.tif")
northness_path <- here(fire_folder_path, "dem", "usgs_10m_northness.tif")
ppt_path <- here(fire_folder_path, "terraclimate", "prefire_ppt.tif")
soil_path <- here(fire_folder_path, "terraclimate", "prefire_soil.tif")
tmax_path <- here(fire_folder_path, "terraclimate", "prefire_tmax.tif")
vpd_path <- here(fire_folder_path, "terraclimate", "prefire_vpd.tif")
pdsi_path <- here(fire_folder_path, "terraclimate", "prefire_PDSI.tif")
prefire_ndvi_path <- here(fire_folder_path, "hls", "prefire_mean_ndvi.tif")
prefire_nbr_path <- here(fire_folder_path, "hls", "prefire_mean_nbr.tif")
dndvi_path <- here(fire_folder_path, "hls", "diff_mean_ndvi.tif")
dnbr_path <- here(fire_folder_path, "hls", "diff_mean_nbr.tif")
out_path <- here(fire_folder_path, paste0(fire_name, "_fire_big_table.csv"))

make_table(buffer_path,
           boundary_path,
           prefire_et_path,
           postfire_et_path,
           elevation_path,
           slope_path,
           aspect_path,
           northness_path,
           tmax_path,
           ppt_path,
           soil_path,
           vpd_path,
           pdsi_path,
           prefire_ndvi_path,
           prefire_nbr_path,
           dndvi_path,
           dnbr_path,
           out_path
           )
```


Next, do feature engineering to match up burned and control points.

- Get control points from median aET in each bucket

```{r}
source(here("scripts","feature_engineering.R"))

# Feature engineering to get control points, aet, and ret
big_table_path <- here(fire_folder_path, paste0(fire_name, "_fire_big_table.csv"))
out_path_with_outliers <- here(fire_folder_path, paste0(fire_name, "_fire_model_df_with_outliers.csv"))
out_path_outliers_removed <- here(fire_folder_path, paste0(fire_name, "_fire_model_df_outliers_removed.csv"))

create_modeling_df(big_table_path, out_path_with_outliers, out_path_outliers_removed)
```

```{r}
# Check the df
df <- vroom(out_path_outliers_removed)

# check point spatial distribution
set.seed(0)  # For reproducibility
sample_size <- 1000  # Number of random points to sample

subset_df <- df %>%
  sample_n(sample_size)

# plot the selected points using ggplot2 with aET shown
ggplot(subset_df, aes(x = lon, y = lat, color = aet)) +
  geom_point() +
  scale_color_viridis_c() +
  theme_minimal() +
  labs(title = "Spatial Distribution of Selected Points", color = "Absolute Evapotranspiration (%)")

# plot histogram of rET
ggplot(final_df, aes(x = ret)) +
  geom_histogram(binwidth = 10, fill = "blue", color = "black") +
  theme_minimal() +
  ggtitle("Distribution of rET")
```

# Train models

Using AWS:

- Upload the scripts and the data

- Run the scripts for training the model on the Creek Fire

# Visualize model results

```{r}
dem <- terra::rast(here("data", "dem", "usgs_10m_dem.tif"))
boundary <- terra::vect(here("data", "boundaries", "creek_fire_boundary.geojson"))

# Plot
ggplot() +
  geom_spatraster(data = dem, aes(fill = usgs_10m_dem)) +
  geom_spatvector(data = boundary, fill = NA, color="white") +
  scale_fill_viridis_c() +
  theme_minimal()

# Find min and max elevations within study area
dem_clipped <- terra::crop(dem, boundary)
min_elev <- min(dem_clipped, na.rm=TRUE)
max_elev <- max(dem_clipped, na.rm=TRUE)
```

